NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-11-07 ms_nihao_budget.tex
modified as the referee's comments except three of them

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas (T$> 10^7$K)
  , inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing mass
  has been relocated past 2 virial radii, and {\bf cool gas dominates
    the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
    while the  warm-hot gas dominates dominates at high mass (M$_{200}
    \gta 3 \times 10^{11} \Msun$)}.  Haloes of mass $\Mhalo\sim
  10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.  More
  massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher fraction
  of their baryons, with $\sim 30\%$ missing, consistent with recent
  observational estimates.  {\bf Moreover, these more massive haloes
    reproduce the observed  fraction of cold, warm-hot and hot gas.
    The fraction of cool gas we predict (0.11) is significantly lower
    than the observation from COS-HALOs (0.3-0.47), but agrees with
    the alternative analysis of \citet{Stern16}}.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy
baryon estimates {\bf (mainly stars and cold gas)} is only 3-8\% of
the big bang nucleosynthesis expectation \citep{Persic92, Fukugita98,
  Bell03, McGaugh10}.  The majority of the cosmic baryons are thought
to be in the form of hot gas around or between galaxies
\citep{Cen09}. Until recently only a fraction of these baryons had
been detected \citep{Bregman07, Shull12}.  This discrepancy is
referred to as the ``missing baryon problem''.  Several theoretical
studies with cosmological simulations have constrained the phase of
the potential reservoirs of the missing baryons {\bf in the
  intergalactic medium (IGM), and find a large fraction of the baryons
  with low density and high temperature resides between galaxies}
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.

The circum galactic medium (CGM) is {\bf another}  major potential
reservoir of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to detect
cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
substantial  portion of the CGM is in the warm or hot phase with
temperature T $> 10^{4.5}$ K.  Gas enters this phase through
photoionization, accretion shocks or shocks caused by galactic winds
\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
the detection is dominated by metal lines, e.g. \ovi{}.  Recent
advances in the detection of gas in the CGM have come  from the COS
survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
significant amount of warm ($10^4 < T < 10^7$K) gas has been detected
\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
future such observations will be extended to a wider range of halo
masses.  A number of large volume cosmological simulations
\citep{Ford13, Ford15, Suresh15b, Oppenheimer16} and zoom-in
cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
given  predictions for the \hi{} and \ovi{} absorption
line. \citet{Gutcke16} compared the column density profile of \ovi{}
and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
cosmological hydrodynamical simulation suite with observations,
studied the covering fraction of dense \hi{}, looked at the shape of
the CGM and its chemical composition. {\bf The simulations
  reproduce  the observational covering fraction and column density
  profile of cool \hi{} well, and recover the observed trends of
  \ovi{} column density with luminosity and impact parameter. In
  common with other simulations, however, the column density of \ovi{}
  is lower and the extent of optically thick \hi{} is smaller than
  observed.}

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
{\bf \citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift $z \approx 0.5-2$ remove a large
amount of gas from the halo. \citet{Voort16} found the baryon fraction
and gas fraction are reduced compared to the cosmic baryon
fraction, especially in low mass haloes.}
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project
\citep{Wang15}.   The initial conditions are created to keep the same
numerical resolution across the whole mass range with typically a
million dark matter particles inside the virial radius of the target
halo at  redshift $z=0$.  The halos to be re-simulated at higher
resolution with baryons have been extracted from 3 different pure
N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.  More
information on the collisionless parent simulations, {\bf the force
  softenings and particle masses for the highest refinement level for
  each simulation} and sample  selection can be found in
\citet{Dutton14} and \citet{Wang15}.

@@

The star formation and feedback modeling follows what was used in the
MaGICC simulations \citep{Stinson13}.   {\bf The gas is converted into
  stars according to the Kennicutt-Schmidt Law when it satisfies a
  temperature and density threshold. Stars feed both metals and energy
  back into the ISM gas surrounding the region where they formed. SN
  feedback is implemented using the blastwave formalism described in
  \citet{Stinson06}. Pre-SN feedback is an attempt to consider
  radiation energy from massive stars. Heating is introduced
  immediately after massive stars form based on how much star light is
  radiated.  Our simulations use thermal feedback to provide pressure
  support and  increase gas temperature above the star formation
  threshold, and thus to decrease star formation.}  There are two
small changes in NIHAO simulations compared to MaGICC:
The change in  number of neighbors
and the new combination of softening length and  particle mass
increases the threshold for star formation from  9.3 to 10.3
cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
  ESF}$, from 0.1 to 0.13.  More details on the star formation and
feedback modeling can be found in \citet{Wang15}.

@@

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
}
\caption{{\bf Comparison between baryon (upper panels) and stellar
    fractions (lower panels) in the NIHAO simulations (blue circles)
    with simulations from \citet{Voort16} (left, red pentagons) and
    \citet{Christensen16} (right, purple pentagons).}}
\label{fig:fire_com}
\end{figure*}

@@

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass (blue points), and the total baryonic
mass including stellar mass plus gas mass (green points).  For the
stellar mass fraction we also show the relations from the halo
abundance  matching \citep{Moster13, Behroozi13, Kravtsov14}.  The
grey area is the one sigma scatter around the mean value  from
\citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all haloes in
our study contain less than the universal fraction of baryons. The
upper panel uses a linear y-axis scale, which highlights the large
amount of baryons that are missing, especially in low mass haloes. The
logarithmic scale in the lower panel highlights the power-law nature
of the relations.

The trends of each component fraction are similar, in that  the
fractions are relatively low in low mass haloes, and increase as the
halo mass increases.  The main difference between the different
components is the slope, with the baryonic mass fraction having a
shallower slope than the stellar mass fraction.  This is because in
low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
the form of gas, while in the highest mass haloes we study
($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amount of gas
has been turned into stars}.

Since most of the haloes we study are above the mass where the cosmic
UV background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons. {\bf
  This is consistent with expectations from energy driven gas
  outflows, where the lower star formation efficiency is more than
  compensated by the shallower potential wells of lower lower mass
  halos according the mass loading factor and circular velocity 
  relaion $\eta \propto V^{-2}$
   \citep[e.g.,][]{Dutton12, Christensen16}.}

@@

{\bf The three most massive galaxies in the NIHAO suite have fairly high
  stellar masses compared to abundance matching results (see blue
  filled circles in Fig.~\ref{fig:budget}), and are thus possibly
  overcooled.  However, they don't significantly bias the baryon
  fraction fitting formula since the high mass slope ($M_{200} >
  10^{11}\Msun$) is constrained by $\sim 40$ other haloes.}

The green shaded region indicates the scatter about the best fit line,
which is 0.151 {\bf dex} for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.052 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.

As might be expected, haloes with the highest masses  we study ($\sim
10^{12}\Msun$) have high baryon fractions ($\sim 0.7$) with relatively
small scatter (0.05 dex). As halo mass decreases, the baryon fraction
decreases and the scatter increases reaching a maximum of $\sim 0.24$
dex in haloes of mass $\sim 4\times10^{10}\Msun$.  However, at the
lowest halo masses we study, below $10^{10}\Msun$, the scatter starts
to decrease. By contrast the scatter in the stellar mass fraction
increases below this scale. Thus it seems unlikely that stellar
feedback is primarily responsible for the low baryon
fractions. Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. {\bf The
  baryon fractions are thus controlled primarily by the halo masses,
  and thus are independent of the large scatter in the star formation
  efficiency.}

@@

\subsubsection{Comparison with other zoom-in simulations}
{\bf In Fig.~\ref{fig:fire_com} we compare the NIHAO results for the
  stellar and baryonic mass fractions with other recent
  state-of-the-art zoom-in simulations from \citet{Voort16} and
  \citet{Christensen16}.  Since these authors both use different halo
  mass definitions than we adopt here, we re-calculate the NIHAO
  results using a virial radius defined at $500\times$ critical
  density (left panels) and $100\times$ critical density (right
  panels).  The simulations analyzed in \citet{Voort16} are from the
  FIRE project \citep{Hopkins14}, which uses a different
  hydrodynamical code and different sub-grid model for star formation
  and feedback. The simulations analyzed in \citet{Christensen16} use
  a similar code as NIHAO, i.e.,  {\sc gasoline}, but with important
  differences. NIHAO uses an upgraded version that improves mixing
  \citep{Keller14}, and includes stronger feedback which was found to
  be necessary to delay star formation at early times
  \citep{Stinson13}. Despite these different codes employed, the
  baryon fractions in the three sets of simulations are in remarkably
  good agreement.

@@

In summary, while the stellar mass fractions are dependent on the
sub-grid models, the baryon fractions (for haloes in the mass range
$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
details of the simulation code. In particular all three codes predict a
greater fraction of missing baryons in lower mass haloes. This
suggests that the potential well of the halo regulates the baryon
fraction more than the strength of the feedback.  }

@@

In Fig.~\ref{fig:corona}, we present the radial distribution of
gas in different phases at $z=0$, normalized to the total baryonic
mass profile, such that, in the region far away from the central galaxy
where the stars are rare, for a given halo the four phases add up to
unity, {\bf each line is colour coded by the virial mass}.  
All simulations share a common attribute.  The cold gas (T$<10^4$K)
is mostly located  near the center  ($R<0.2R_{200}$)
where most stars in galaxies form.  In contrast, the cool ($10^4$K$<$T$<10^5$K)
and  warm-hot ($10^5$K$<$T$<10^7$K) gas are
located at large distances with roughly constant fractions up to 2
times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
for all galaxies in the NIHAO sample, with the maximum hot gas
fraction at any radius being  less than 5\%.

Despite these similarities, we find a considerably higher proportion
of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$) in the
whole corona region.  For higher mass galaxies, warm-hot gas dominates
the corona  which signals {\bf stronger virial shocks} and higher
efficiency  of feedback.  Even beyond the virial radius, the cool and
warm-hot gas has similar features as the gas within virial radius
which reveals the gas surrounding galaxies within large distances is
the major reservoir of baryons.

@@

Fig.~\ref{fig:rps} shows the {\bf cumulative fraction} of total baryons  for
each simulation. Here the y-axis is the ratio between the baryonic to
dark matter mass, $M_{\rm b}(<R) / M_{\rm dm}(<R)$, enclosed
within a sphere of radius, $R$, normalized by the cosmic
baryon-to-dark matter ratio, $\Omega_{\rm b}/\Omega_{\rm dm}$.

@@

Each solid curve represents a halo, and the curves are coloured by
their halo mass (red for high masses to blue for low masses).  Broadly
speaking, the curves have a similar shape, with a normalization that
depends on halo mass. They have a cusp in  the central region where
the stars and cold gas dominate, then become flat in the outer region.
More massive haloes have higher baryon fractions at all radii.  At
small radii, the baryon to dark matter ratio is higher than the cosmic
value due to gas dissipation. {\bf Beyond 0.5 virial radii, all haloes
  are missing baryons.}  Even beyond the virial radius, there is
little change in the baryon fraction up to 2 virial radii.  We thus
conclude that the missing baryons are well outside of the virial
radius.

{\bf \citet{Ford16} compare results for the cumulative baryon profile
  from two cosmological hydrodynamic simulations which employed
  different prescriptions for galactic  outflow models. They
  constructed samples of simulated galaxies with a similar
  distribution of stellar masses to that of COS-Halos.

@@

The simplified constant wind outflow model (``cw'') shows
a lower fraction at all radii inside $\Rvir$, even though the ``ezw'' 
and ``cw'' models generally gives similar observational absorption 
line properties. This suggests that the cumulative baryon
fraction profile is complementary to the total amount of CGM gas for
distinguishing between competing outflow models.
}

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes.
Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
function of the virial mass. In physical units, we find that the
baryon radius generally increases with virial mass. {\bf When
  normalized by the virial radius, the distance baryons are ejected
  gradually decreases as halo mass increases, varying from
  $\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$
  to $\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.}

@@

{\bf We hope our results will motivate observers to obtain more
  accurate measurements of the mass fractions in different phases of
  the CGM over a wide range of galaxy masses, and simulators to make
  the corresponding predictions.}

>>>>

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas (T$> 10^7$K)
  , inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing mass
  has been relocated past 2 virial radii, and cool gas dominates
    the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
    while the  warm-hot gas dominates at high mass (M$_{200}
    \gta 3 \times 10^{11} \Msun$).  Haloes of mass $\Mhalo\sim
  10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.  More
  massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher fraction
  of their baryons, with $\sim 30\%$ missing, consistent with recent
  observational estimates.  Moreover, these more massive haloes
    reproduce the observed  fraction of cold, warm-hot and hot gas.
    The fraction of cool gas we predict (0.11) is significantly lower
    than the observation from COS-HALOs (0.3-0.47), but agrees with
    the alternative analysis of \citet{Stern16}.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy
baryon estimates (mainly stars and cold gas) is only 3-8\% of
the big bang nucleosynthesis expectation \citep{Persic92, Fukugita98,
  Bell03, McGaugh10}.  The majority of the cosmic baryons are thought
to be in the form of hot gas around or between galaxies
\citep{Cen09}. Until recently only a fraction of these baryons had
been detected \citep{Bregman07, Shull12}.  This discrepancy is
referred to as the ``missing baryon problem''.  Several theoretical
studies with cosmological simulations have constrained the phase of
the potential reservoirs of the missing baryons in the
  intergalactic medium (IGM), and find a large fraction of the baryons
  with low density and high temperature resides between galaxies
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.

{\bf As a part of the IGM, the circum galactic medium (CGM) is always 
treated as }an major potential
reservoir of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to detect
cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
substantial  portion of the CGM is in the warm or hot phase with
temperature T $> 10^{4.5}$ K.  Gas enters this phase through
photoionization, accretion shocks or shocks caused by galactic winds
\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
the detection is dominated by metal lines, e.g. \ovi{}.  Recent
advances in the detection of gas in the CGM have come  from the COS
survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
significant amount of warm ($10^4 < T < 10^7$K) gas has been detected
\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
future such observations will be extended to a wider range of halo
masses.  A number of large volume cosmological simulations
\citep{Ford13, Ford15, Suresh15b, Oppenheimer16} and zoom-in
cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
given  predictions for the \hi{} and \ovi{} absorption
line. \citet{Gutcke16} compared the column density profile of \ovi{}
and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
cosmological hydrodynamical simulation suite with observations,
studied the covering fraction of dense \hi{}, looked at the shape of
the CGM and its chemical composition. The simulations
  reproduce  the observational covering fraction and column density
  profile of cool \hi{} well, and recover the observed trends of
  \ovi{} column density with luminosity and impact parameter. In
  common with other simulations, however, the column density of \ovi{}
  is lower and the extent of optically thick \hi{} is smaller than
  observed.

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
\citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift $z \approx 0.5-2$ remove a large
amount of gas from the halo. {\bf Several simulations 
\citep{Crain10, Christensen16,Voort16}} found the baryon fraction
and gas fraction are reduced compared to the cosmic baryon
fraction, especially in low mass haloes.
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project
\citep{Wang15}.   The initial conditions are created to keep the same
numerical resolution across the whole mass range with typically a
million dark matter particles inside the virial radius of the target
halo at  redshift $z=0$.  The halos to be re-simulated at higher
resolution with baryons have been extracted from 3 different pure
N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.  
{\bf Dark matter particle masses range from $\sim 10^3 \Msun$ in 
our lowest mass haloes to $\sim 10^5 \Msun$ in our most massive 
haloes, and their force softenings range from $\sim$ 100 pc in 
low mass range to $\sim$ 900 pc in high mass range.
Gas particles are less massive in factor of 5 correspondingly, and
the force softenings are 3 times less than dark matters.}
More information on the collisionless parent simulations, the force
  softenings and particle masses for the highest refinement level for
  each simulation and sample  selection can be found in
\citet{Dutton14} and \citet{Wang15}.

@@

The star formation and feedback modeling follows what was used in the
MaGICC simulations \citep{Stinson13}.   The gas is converted into
  stars according to the Kennicutt-Schmidt Law when it satisfies a
  temperature and density threshold. Stars feed both metals and energy
  back into the ISM gas surrounding the region where they formed. SN
  feedback is implemented using the blastwave formalism described in
  \citet{Stinson06}. Pre-SN feedback is an attempt to consider
  radiation energy from massive stars. Heating is introduced
  immediately after massive stars form based on how much star light is
  radiated.  Our simulations use thermal feedback to provide pressure
  support and  increase gas temperature above the star formation
  threshold, and thus to decrease star formation.  There are two
small changes in NIHAO simulations compared to MaGICC:
The change in  number of neighbors
and the new combination of softening length and  particle mass
increases the threshold for star formation from  9.3 to 10.3
cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
  ESF}$, from 0.1 to 0.13.  More details on the star formation and
feedback modeling can be found in \citet{Wang15}.

@@

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
}
\caption{Comparison between baryon (upper panels) and stellar
    fractions (lower panels) in the NIHAO simulations (blue circles)
    with simulations from \citet{Voort16} (left, red pentagons) and
    \citet{Christensen16} (right, purple pentagons).}
\label{fig:fire_com}
\end{figure*}

@@

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass {\bf within 20\% $\Rvir$} (blue points), 
and the total baryonic
mass including stellar mass plus gas mass (green points).  For the
stellar mass fraction we also show the relations from the halo
abundance  matching \citep{Moster13, Behroozi13, Kravtsov14}.  The
grey area is the one sigma scatter around the mean value  from
\citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all haloes in
our study contain less than the universal fraction of baryons. The
upper panel uses a linear y-axis scale, which highlights the large
amount of baryons that are missing, especially in low mass haloes. The
logarithmic scale in the lower panel highlights the power-law nature
of the relations.

The trends of each component fraction are similar, in that  the
fractions are relatively low in low mass haloes, and increase as the
halo mass increases.  The main difference between the different
components is the slope, with the baryonic mass fraction having a
shallower slope than the stellar mass fraction.  This is because in
low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
the form of gas, while in the highest mass haloes we study
($\Mhalo\sim 10^{12}\Msun$) a substantial amount of gas
has been turned into stars.

Since most of the haloes we study are above the mass where the cosmic
UV background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons. 
  This is consistent with expectations from energy driven gas
  outflows, where the lower star formation efficiency is more than
  compensated by the shallower potential wells of lower lower mass
  halos according {\bf to} the mass loading factor and circular velocity 
  {\bf relation }$\eta \propto V^{-2}$
   \citep[e.g.,][]{Dutton12, Christensen16}.

@@

  The three most massive galaxies in the NIHAO suite have fairly high
  stellar masses compared to abundance matching results (see blue
  filled circles in Fig.~\ref{fig:budget}), and are thus possibly
  overcooled.  However, they don't significantly bias the baryon
  fraction fitting formula since the high mass slope ($M_{200} >
  10^{11}\Msun$) is constrained by $\sim 40$ other haloes.

The green shaded region indicates the scatter about the best fit line,
which is 0.151 dex for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.052 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.

As might be expected, haloes with the highest masses  we study ($\sim
10^{12}\Msun$) have high baryon fractions ($\sim 0.7$) with relatively
small scatter (0.05 dex). As halo mass decreases, the baryon fraction
decreases and the scatter increases reaching a maximum of $\sim 0.24$
dex in haloes of mass $\sim 4\times10^{10}\Msun$.  However, at the
lowest halo masses we study, below $10^{10}\Msun$, the scatter starts
to decrease. By contrast the scatter in the stellar mass fraction
increases below this scale. Thus it seems unlikely that stellar
feedback is primarily responsible for the low baryon
fractions. Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. The
  baryon fractions {\bf in low mass haloes} are thus controlled primarily 
  by the halo masses,
  and thus are independent of the large scatter in the 
  {\bf stellar mass}.

@@

\subsubsection{Comparison with other zoom-in simulations}
  In Fig.~\ref{fig:fire_com} we compare the NIHAO results for the
  stellar and baryonic mass fractions with other recent
  state-of-the-art zoom-in simulations from \citet{Voort16} and
  \citet{Christensen16}.  Since these authors both use different halo
  mass definitions than we adopt here, we re-calculate the NIHAO
  results using a virial radius defined at $500\times$ critical
  density (left panels) and $100\times$ critical density (right
  panels).  The simulations analyzed in \citet{Voort16} are from the
  FIRE project \citep{Hopkins14}, which uses a different
  hydrodynamical code and different sub-grid model for star formation
  and feedback. The simulations analyzed in \citet{Christensen16} use
  a similar code as NIHAO, i.e.,  {\sc gasoline}, but with important
  differences. NIHAO uses an upgraded version that improves mixing
  \citep{Keller14}, and includes stronger feedback which was found to
  be necessary to delay star formation at early times
  \citep{Stinson13}. Despite these different codes employed, the
  baryon fractions in the three sets of simulations are in remarkably
  good agreement.

@@

In summary, while the stellar mass fractions are dependent on the
sub-grid models, the baryon fractions (for haloes in the mass range
$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
details of the simulation code. In particular all three codes predict a
greater fraction of missing baryons in lower mass haloes. This
suggests that the potential well of the halo regulates the baryon
fraction more than the strength of the feedback.

@@

In Fig.~\ref{fig:corona}, we present the radial distribution of
gas in different phases at $z=0$, normalized to the total baryonic
mass profile, such that, in the region far away from the central galaxy
where the stars are rare, for a given halo the four phases add up to
unity, each line is colour coded by the virial mass.  
All simulations share a common attribute.  The cold gas (T$<10^4$K)
is mostly located  near the center  ($R<0.2R_{200}$)
where most stars in galaxies form.  In contrast, the cool ($10^4$K$<$T$<10^5$K)
and  warm-hot ($10^5$K$<$T$<10^7$K) gas are
located at large distances with roughly constant fractions up to 2
times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
for all galaxies in the NIHAO sample, with the maximum hot gas
fraction at any radius being  less than 5\%.

Despite these similarities, we find a considerably higher proportion
of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$) in the
whole corona region.  For higher mass galaxies, warm-hot gas dominates
the corona  which signals stronger virial shocks and higher
efficiency  of feedback.  Even beyond the virial radius, the cool and
warm-hot gas has similar features as the gas within virial radius
which reveals the gas surrounding galaxies within large distances is
the major reservoir of baryons.

@@

Fig.~\ref{fig:rps} shows the cumulative fraction of total baryons  for
each simulation. Here the y-axis is the ratio between the baryonic to
dark matter mass, $M_{\rm b}(<R) / M_{\rm dm}(<R)$, enclosed
within a sphere of radius, $R$, normalized by the cosmic
baryon-to-dark matter ratio, $\Omega_{\rm b}/\Omega_{\rm dm}$.

@@

Each solid curve represents a halo, and the curves are coloured by
their halo mass (red for high masses to blue for low masses).  Broadly
speaking, the curves have a similar shape, with a normalization that
depends on halo mass. They have a cusp in  the central region where
the stars and cold gas dominate, then become flat in the outer region.
More massive haloes have higher baryon fractions at all radii.  At
small radii, the baryon to dark matter ratio is higher than the cosmic
value due to gas dissipation. Beyond 0.5 virial radii, all haloes
  are missing baryons.  Even beyond the virial radius, there is
little change in the baryon fraction up to 2 virial radii.  We thus
conclude that the missing baryons are well outside of the virial
radius.

 \citet{Ford16} compare results for the cumulative baryon profile
  from two cosmological hydrodynamic simulations which employed
  different prescriptions for galactic  outflow models. They
  constructed samples of simulated galaxies with a similar
  distribution of stellar masses to that of COS-Halos.

@@

The simplified constant wind outflow model (``cw'') shows
a lower fraction at all radii inside $\Rvir$, even though the ``ezw'' 
and ``cw'' models generally gives similar observational absorption 
line properties. This suggests that the cumulative baryon
fraction profile is complementary to the total amount of CGM gas for
distinguishing between competing outflow models.

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes,
{\bf and is a radius within the effective volume of the simulations
since contamination fraction in a shell between 0.9 and 
1.0 $\Rbar$ shows most NIHAO galaxies have a fraction close to 0,
with largest only around 10 - 20. }
Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
function of the virial mass. In physical units, we find that the
baryon radius generally increases with virial mass. When
  normalized by the virial radius, the distance baryons are ejected
  gradually decreases as halo mass increases, varying from
  $\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$
  to $\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.

@@

 We hope our results will motivate observers to obtain more
  accurate measurements of the mass fractions in different phases of
  the CGM over a wide range of galaxy masses, and simulators to make
  the corresponding predictions.
